Our Title

### 2015-05-05 draft.tex
Moved pre-detonation nuclear forensics from Ch 6 to Ch 5.

@@

@@

\subsection{????? Need short paragraph discussion on pre-detonation nuclear forensics. ?????}

@@

Reference on Drive: Forensic questions you can answer (in the fission folder).

@@

\subsection{Pre-Detonation Nuclear Forensics}

\subsubsection{?????? This section hasn't been created yet  ???????}

\subsubsection{??????  Add ref to this Tech Appendix, once it's done   ??????}

>>>>

\enquote{One of the most important lessons of the Cold War was that incessantly worrying about the low-probability / high-impact cases was a mistake.}  - Kenneth Pollack \cite{pollack2014unthinkable}

The ISIL nuclear threat is, by definition, a low-probability/high-impact case as this report has shown.  Developing nuclear weapons amidst crippling sanctions, airstrikes, and a dedicated opposition has never been done, despite several nation states attempting to do so.  Therefore, we choose to not repeat the mistakes of history and propose that no changes to U.S. policy be implemented to prevent ISIL from obtaining NWs.

@@

\section{Pre-Detonation Nuclear Forensics}

\subsection{?????? This section hasn't been created yet  ???????}

\subsection{??????  Add ref to this Tech Appendix, once it's done   ??????}

@@

@@

@@
